---
title: "Generating_RunoffCoeff_Baseflow"
author: "kj"
date: "9/23/2020"
output: html_document
    toc: true
    number_sections: true
---
# Creating Baseflow and Stormflow Rasters
This Rmd explains the data sources and processing to create these rasters for NECN.<br>

## Data Sources Used
***Baseflow Data Sources:***<br>

1) An existing baseflow baster<br>
Downloaded here: https://water.usgs.gov/GIS/metadata/usgswrd/XML/bfi48grd.xml<br>
    -This dataset was simply downloaded and resampled. We did not have an existing baseflow raster. 

***Stormflow Data Sources:***<br>

1) SSURGO Soils Data <br>
Downloaded here: https://water.usgs.gov/GIS/metadata/usgswrd/XML/bfi48grd.xml<br>
    -This dataset was simply downloaded and resampled. We did not have an existing baseflow raster. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


```




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
